Large squeezing in Bose-Einstein condensates with large numbers of atoms

### 2013-07-18 large_number_squeezing_with_atoms.tex
More changes to the \pi pulse section.

Modal mismatch is generated by the different atomic potentials seen by the two internal states.  A straightforward method of minimising this effect in the case that modes $\ket{a}$ and $\ket{b}$ are equally occupied after the initial coupling pulse is to apply a $\pi$-pulse to swap the populations of the internal states after half of the evolution.  As can be seen by Eqs.~\eqref{eqa1} and \eqref{eqb1}, such a pulse also leaves the quantum statistics of each state unchanged.  The idea of this scheme is to make the effective potential seen by the atoms in state $\ket{a}$ during the second half of the hold time very similar to that seen by the atoms that were in state $\ket{a}$ during the first half of the hold time.  In the limit of short hold times and for equal occupations of the two modes, this technique reduces the difference in the mode shapes after the hold time.  In practice this will never work perfectly --- due to the density distributions of $\psi_a(\mathbf{r})$ and $\psi_b(\mathbf{r})$ not being in the ground state, their mode shapes will have changed by the time the $\pi$-pulse is applied, and so the spatial dynamics in the second half of the hold time will not be quite the same as those during the first half.  Nonetheless, in many regimes, such a $\pi$-pulse can produce some improvement.  More importantly, as this scheme accepts that the two modes will change shape, and attempts to make them change in a similar fashion, it allows the possibility of much longer hold times. That is, if we are no longer constrained to hold times short enough such that the mode shapes of the atoms in states $|a \rangle$ and $|b \rangle$ do not change significantly, much more squeezing can be extracted from the system.

>>>>

Modal mismatch is generated by the different atomic potentials seen by the two internal states.  A straightforward method of minimising this effect is to apply a $\pi$-pulse to swap the populations of the internal states after half of the evolution.  As can be seen by Eqs.~\eqref{eqa1} and \eqref{eqb1}, such a pulse also leaves the quantum statistics of each state unchanged.  The idea of this scheme is to make the effective potential seen by the atoms in state $\ket{a}$ during the second half of the hold time very similar to that seen by the atoms that were in state $\ket{a}$ during the first half of the hold time, and will only work if the modes $\ket{a}$ and $\ket{b}$ have an equal occupation at the start of the hold time, or if $\chi_+=\chi_{aa} + \chi_{bb} - 2\chi_{ab}=0$.  In the latter case, this reduces to a spin-echo pulse, and as the squeezing effects of the $\Delta\omega$ term in Eq.~\eqref{eqNonlinearJosephson} are cancelled in this case, there will be no squeezing.  However, in the limit of short hold times, for equal occupations of the two modes, and when $\chi_+\neq 0$, this technique reduces the difference in the mode shapes after the hold time.  In practice this will never work perfectly --- due to the density distributions of $\psi_a(\mathbf{r})$ and $\psi_b(\mathbf{r})$ not being in the ground state, their mode shapes will have changed by the time the $\pi$-pulse is applied, and so the spatial dynamics in the second half of the hold time will not be quite the same as those during the first half.  Nonetheless, in many regimes, such a $\pi$-pulse can produce some improvement.  More importantly, as this scheme accepts that the two modes will change shape, and attempts to make them change in a similar fashion, it allows the possibility of much longer hold times. That is, if we are no longer constrained to hold times short enough such that the mode shapes of the atoms in states $|a \rangle$ and $|b \rangle$ do not change significantly, much more squeezing can be extracted from the system.
